% !TeX root = ../thuthesis-example.tex

% 中英文摘要和关键字

\begin{abstract}
  中微子与原子核的相干弹性散射（CE$\nu$NS）是一种标准模型下的粒子物理过程。
  本文对以核反应堆作为中微子源、使用液氙时间投影室探测器和高纯锗探测器测量该过程的灵敏度进行了预测。
  通过设计建造一个极低阈值、极低本底并可在地面附近运行的液氙时间投影室，
  电子反冲本底预计可以压低至0.1$\left(\si{kg}\cdot\si{day}\cdot\si{keV}\right)^{-1}$水平，
  $\mu$子引起的核反冲本底可以压低至0.5$\left(\si{kg}\cdot\si{day}\right)^{-1}$水平。
  在一台堆芯热功率250$\si{GW}$商业发电反应堆运行一年，30千克量级的液氙时间投影室探测器预计探测到超过3000个CE$\nu$NS信号。
  通过设计建造一台本底水平与CDEX-10类似的5千克高纯锗探测器，在同等条件下，预计探测到超过1000个CE$\nu$NS信号。
  利用探测器到的CE$\nu$NS过程，两种探测器对中微子超标准模型有效相互作用和低动量转移下的弱混合角的测量将填补实验空白或达到国际先进水平。

  % 关键词用“英文逗号”分隔，输出时会自动处理为正确的分隔符
  \thusetup{
    keywords = {中微子与原子核的相干弹性散射, 灵敏度预测, 本底模拟, 超标准模型有效相互作用},
  }
\end{abstract}

\begin{abstract*}
  An abstract of a dissertation is a summary and extraction of research work and contributions.
  Included in an abstract should be description of research topic and research objective, brief introduction to methodology and research process, and summary of conclusion and contributions of the research.
  An abstract should be characterized by independence and clarity and carry identical information with the dissertation.
  It should be such that the general idea and major contributions of the dissertation are conveyed without reading the dissertation.

  An abstract should be concise and to the point.
  It is a misunderstanding to make an abstract an outline of the dissertation and words “the first chapter”, “the second chapter” and the like should be avoided in the abstract.

  Keywords are terms used in a dissertation for indexing, reflecting core information of the dissertation.
  An abstract may contain a maximum of 5 keywords, with semi-colons used in between to separate one another.

  % Use comma as separator when inputting
  \thusetup{
    keywords* = {keyword 1, keyword 2, keyword 3, keyword 4, keyword 5},
  }
\end{abstract*}
